Prepare Data

### 2025-09-03 src/analysis/Analysis.Rmd
Updated figures, small changes intro and abtract
update Compendium, final submission

# Analyses
```{r "data for analyses"}
load(here("data/intermediate/cleaned_data_joined.RData"))
```

@@

```{r "balance-checks", fig.height=12, fig.width=8}
source(here("src/analysis/balance-test.R"))
df
```

## Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b
rm(b_b, b1, b2, df, df_nl, df_us, tmp)
```

```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i
rm(b1, b2, df, df_nl, df_us, tmp, issues_nl, issues_us, i)
```

## Ideological Bias hypothesis
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1a
p1b

(p1b_1+p1b_2)/(p1b_3 + p1b_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom')
rm(df, df_nl, df_us, h1a, h1b, p1b_1, 
   pred1b_1, pred1b_2, pred1b_3, pred1b_4, tmp)
```

## Overinterpretation Hypotheses
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2a
p2b
p2c1
p2c2

## Masking Hypothesis
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3a
p3b
p3c1
p3c2

## Exploration
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R"))
p_b1
p_b2
p_e1a
p_e1b
p_e1c
```

```{r "explore-profiles", fig.height=10, fig.width=15}
source(here("src/analysis/profiles.R"))
prof1 
prof2
```

@@

>>>>

# Analyses
```{r "data for analyses"}
load(here::here("data/intermediate/cleaned_data_joined.RData"))
```

@@

```{r "balance-checks", fig.height=12, fig.width=8}
source(here("src/analysis/balance-test.R"))
df #Figure OA3
```

#Descriptives: Profiles
```{r "explore-profiles", fig.height=10, fig.width=15}
source(here("src/analysis/profiles.R"))
prof1 #Figure 2
prof2 #Figure 3
```

@@

## Ideological Bias hypothesis (H1)
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1a #Figure 4a
p1b #Figure 4b

(p1b_1+p1b_2)/(p1b_3 + p1b_4) + 
  plot_layout(guides = "collect") & theme(legend.position = 'bottom') #Figure 4b
rm(df, df_nl, df_us, h1a, h1b, p1b_1, 
   pred1b_1, pred1b_2, pred1b_3, pred1b_4, tmp)
```

## Overinterpretation Hypotheses (H2)
```{r "h2", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h2.R"))
p2a #Figure 5
p2b
p2c1
p2c2

## Masking Hypothesis (H3)
```{r "h3", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h3.R"))
p3a #Figure 6
p3b
p3c1
p3c2

## Exploration

### Issues effect
```{r "issues", fig.align="center", fig.height=16, fig.width=8}
source(here("src/analysis/issue_specific.R"))
b_i #Figure OA.4
rm(b1, b2, df, df_nl, df_us, tmp, issues_nl, issues_us, i)
```

### Baseline Model
```{r "baseline", fig.align="center", fig.height=4, fig.width=8}
source(here("src/analysis/baseline.R"))
b #Figure OA.5
rm(b_b, b1, b2, df, df_nl, df_us, tmp)
```

### Different ways of measuring ideological distance
```{r "exploration", fig.height=7, fig.width=8}
source(here("src/analysis/exploration.R")) #Figures OA.6
p_b1
p_b2
p_e1a
p_e1b
p_e1c
```

### 2025-09-03 src/data-processing/prepare-data.Rmd
update Compendium, final submission

```{r "get & clean data", results="hide"}
#Load Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))

@@

## Save Data for Analysis
```{r "save data"}
save(d, file = here("data/intermediate/cleaned_data_joined.RData"))
```

@@

### Dependent Variable by Issue
```{r "Dependent Variable", echo=F, fig.width=15, fig.height=10}
p1a <- d |> 
  filter(country == "NL") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_nlp,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_nlp) |> 
  mutate(stance_nlp = recode(stance_nlp,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_nlp)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "",
       title = "NL Data - Strict Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

@@

### Covariates
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=6, fig.height=6}
rm(p1a, p1b, p2a, p2b)
p <- d %>% 
  filter(country=="NL") |> 
  select(distance, PT7, PT6) %>% 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Left/Liberal, 1 = Right/Conservative)",
                       `PT7` = "Political Knowledge \n(0 = Low, 1 = High)"),
         country = "The Netherlands")

>>>>

```{r "get & clean data", results="hide", eval=FALSE}
#Load Dutch Data
d_nl <- read_sav(here("data/raw-private/NLOZ2206_Mariken_Bias-experiment.sav"))

@@

## Save Data for Analysis
```{r "save data", eval=FALSE}
save(d, file = here("data/intermediate/cleaned_data_joined.RData"))
rm(d_nl, d_us)
```

@@

### Dependent Variable by Issue
```{r "Dependent Variable", echo=F, fig.width=15, fig.height=10}
load(here("data/intermediate/cleaned_data_joined.RData"))
p1a <- d |> 
  filter(country == "NL") |> 
  mutate(issue2 = recode(issue,
                         `tax on carbon emissions` = "Climate",
                         `a wealth tax for the richest Americans` = "Tax",
                         `the tax system` = "Tax",
                         `military presence in the Pacific Ocean` = "EU/Foreign Policy",
                         `military build-up in the Pacific Ocean` = "EU/Foreign Policy",
                         `immigranten` = "Immigration",
                         `immigratie` = "Immigration",
                         `het tegengaan van stikstofuitstoot` = "Climate",
                         `het stikstofbeleid` = "Climate",
                         `het verhogen van het belastingstarief voor de hoogste inkomens` = "Tax",
                         `het belastingstelsel` = "Tax",
                         `de  rol van Nederland in de Europese Unie` = "EU/Foreign Policy",
                         `het lidmaatschap van de Europese Unie voor Nederland` = "EU/Foreign Policy")) |> 
  group_by(stance_nlp,issue2,specified, masking, country) %>% 
  count() %>% 
  drop_na(stance_nlp) |> 
  mutate(stance_nlp = recode(stance_nlp,
                             `correct` = "Correct",
                             `incorrect` = "Incorrect"),
         specified = ifelse(specified == "Specified", 
                                "Condition: Specified Sentence", "Underspecified Sentence"),
         masking = ifelse(masking == 1, "Actor Masked", "Party Revealed")) %>% 
  ggplot(aes(y = issue2, x = n, fill = stance_nlp)) +
  geom_col() +
  facet_grid(masking~specified) +
  labs(x = "", y = "",
       title = "NL Data - Strict Interpretation") +
  #scale_x_continuous(labels = scales::percent) +
  theme_ipsum() +
  scale_fill_manual(values = fig_cols[c(3, 2)]) +
  theme(legend.position = "bottom",
        legend.title = element_blank())

@@

### Covariates
```{r "Independent Variables", echo=F, message=FALSE, warning=FALSE,fig.width=6, fig.height=6}
rm(p1a, p1b, p2a, p2b)

p <- d %>% 
  filter(country=="NL") |> 
  select(distance, PT7, PT6) %>% 
  pivot_longer(cols = everything(),
               values_to = "score") %>% 
  group_by(name) %>% 
  summarise(m = mean(score),
            stdev = sd(score)) %>% 
  mutate(name = recode(name,
                       `distance` = "Ideological Distance \n(> = More Distance)",
                       `PT6` = "Ideological Self Placement \n(0 = Left/Liberal, 1 = Right/Conservative)",
                       `PT7` = "Political Knowledge \n(0 = Low, 1 = High)"),
         country = "The Netherlands")
